---
title: "PHC410 (Pharmaceutical Biostatistics)"
subtitle: "Data Cleaning and Transformation: Practice"
author: 
  - <put your name here> <your student ID> - <your group>
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document: default
  html_document: default
---

# Activity

1. Load `dplyr` and `haven` packages.

My code:
```{r results='hide', collapse=TRUE}
#put your code down here after this line

```

2. Import SAS transport file `subs_nhanes1718.xpt` from your `input` folder into your RStudio. Assign the object as `nhanes`.

My code:
```{r , collapse=TRUE}
#put your code down here after this line


```


3. Print the column names and display the structure of `nhanes`. 

My code:
```{r , collapse=TRUE}
#put your code down here after this line


```


4. Using the following names, replace the column names and save your changes to `nhanes`:

    + `RIAGENDR` as Gender
    + `DMDCITZN` as Citizenship
    + `DMDHREDZ` as EducationL
    + `DMDHRMAZ` as MaritalS
    + `DMDHRAGZ` as Age
    + `INDFMPIR` as PovertyR

My code:
```{r collapse=TRUE}
#put your code down here after this line


```


5. Based on the description in `nhanes_desc.txt`, recode `Gender`, `Citizenship`, `EducationL` and `MaritalS` (use `recode_factor` when appropriate).

My code:
```{r collapse=TRUE}
#put your code down here after this line

```

6. Using `pipe` function, display the sequence no, education level and poverty-income ratio for the first 10 male participants.
    
My code:
```{r collapse=TRUE}
#put your code down here after this line

```

7. Count the number of female and male in `nhanes`, grouped by education level. State the number of college graduates according to their gender.
    
My code:
```{r collapse=TRUE}
#put your code down here after this line

```

Answer: No. of college graduates; (1) Male: ?    , (2) Female: ?


8. Identify the number of rows in `nhanes` without missing values. State the total number.
    
My code:
```{r collapse=TRUE}
#put your code down here after this line

```

Answer: Total number of rows: ?