---
title: "PHC410 (Pharmaceutical Biostatistics)"
subtitle: "Parametric Statistical Techniques: Practice"
author: 
  - <put your name here> <your student ID> - <your group>
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document: default
  html_document: default
---


1. Using the description in `cvd_train_desc.txt`, recode all categorical variables of `cvd_train` into factor. Assign variable as ordinal where appropriate. 

```{r collapse=TRUE, warning=FALSE}

```

2. Does the systolic blood pressures differ between patients with and without cardiovascular disease? State your hypothesis, perform appropriate tests and interpret your findings for each test.

a) Hypothesis:  

H$_{0}$: 

H$_{a}$: 


b) Perform appropriate tests.

```{r collapse=TRUE}




```


c) Interpret your findings for each test. 





3. Does the weight of patients differ between different glucose level? Using appropriate tests, determine whether the differences are statistically significant. Assume that the variances between groups are equal. 

a) State your hypothesis 





b) Perform appropriate tests. 

```{r collapse=TRUE}


```


c) Interpret your findings for all applicable tests. 


