---
title: "PHC410 (Pharmaceutical Biostatistics)"
subtitle: "Exploratory Data Analysis (EDA): Practice"
author: 
  - <put your name here> <your student ID> - <your group>
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document: default
  html_document: default
---


1. Import `WHO_suicide.csv` from `input` folder and assign to an object `subs_suicide`.

```{r}
#put your code down here after this line
```

2. Observe the structure of `subs_suicide`. Convert categorical variables in the data set as factors.

```{r}
#put your code down here after this line

```

3. Determine and interpret the measure of central tendency for `year`. Load a suitable package if required.

```{r}
#put your code down here after this line

```

4. Using only single line of codes, find the mean, lower, and upper quartiles for the number of suicides per 100k population for Australia in year 2015. 

```{r}
#put your code down here after this line

```
Answer: (put your answer here).


5. Choose one variable from `subs_suicide` and create a boxplot using the variable. Explain the range and the skewness of the variable.

```{r}
#put your code down here after this line

```
Answer: (put your answer here).



6. Create a scatter plot between `gdp` and `suicide_100_population`. Interpret the relationship between the two variables from the graph.

```{r collapse=TRUE}
#put your code down here after this line
```
Interpretation: (put your answer here)


7. Create both stacked and group bar charts that represent the age and the types of generation. Display the legend and set the title of legend as `Age group`. Use `rainbow(6)` as the colours and set a smaller size of x axis labels with `cex.names=0.6`.

```{r collapse=TRUE}
#put your code down here after this line
```

8. Based on your results in question 4, which generation has the highest number of age groups who had attempted suicide?

Answer: (put your answer here)